---
title: 'Data Science Capstone Report #1'
author: "José Gustavo Zagato Rosa"
date: "07/05/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Milestone Report 
### Introduction and Objectives

The main goal of this report is to demonstrate the the capacity developed to handle unstructred data in order to produce a structured set of records which can then be used for the purposes of statistical modeling in the relms of Text Mining. 

Due the size of the provided raw files I took the approach to structure different scripts to handle specific steps of the entire process. for more detais, please refer to my gitrepo wich contains the whole project. [getrepo](https://github.com/jguszr/DSCapstone)

I also tried to use as much as possible of the  [TM R](https://cran.r-project.org/web/packages/tm/index.html)  package among with its plugins for multicore processing (which, at this time I still developing).

### The Process

I approach this project from a streamline point of view, in which I separete different objectives in diferent files. So at this point the project contains 4 folder structures as follows

* **data** : Contains a individual folder for each step of the process, from raw file to Ngram Files
* **Prepare** : Contains the R Scripts to download and setup the local systems *data* structure and split the raw data into smaller sampler files. the File itself can be found [here](https://github.com/jguszr/DSCapstone/blob/master/Prepare/prepareData.R)

* **Exploratory** : Contains the R Scripts That I used to learn the TM package among some preliminary studies regarding the data it self. 

* **Exploratory** : Contains the R Scripts That I used to learn the TM package among some preliminary studies regarding the data it self. check the file [here](https://github.com/jguszr/DSCapstone/blob/master/Exploratory/CorseExplorer.R)

* **ngramGennerator** : Contains the R Scripts That I used to process the short files (previously generated by the Prepare script) into DocumentTermMatrix into three new CVS files containing the frequency of the most comon Ngram in question.[here](https://github.com/jguszr/DSCapstone/blob/master/ngramGennerator/nGramGenerator.R)

### The overall process 

Idealistically you can run the scripts in the following squence to archive the same result I got.

* **Prepare** : [Prepare everything] (https://github.com/jguszr/DSCapstone/blob/master/Prepare/prepareData.R)

* **ngramGennerator** : [Generate the Ngrams] (https://github.com/jguszr/DSCapstone/blob/master/Prepare/prepareData.R)

This two steeps will get the __.cvs__ files containg Ngram frequencies.


## And now some initial analisys

### loading the Libraries 
```{r}
require(tm)
require(RWeka)

```

Using a VCorpus tm object to load all files in german. 

```{r building Corpus, warning=FALSE}
setwd("~/Documents/coursera/datasciencecoursera/DSCapstone")
corpus <- VCorpus(DirSource("./data/short",pattern = "^de_DE",encoding = "UTF-8"),
                   readerControl = list(reader= readPlain,language="de",load=TRUE))
```

After it we can use the __inspect__ and the __meta__ tm functions to check data and metadata of a specific corpus property, or have a full view of it using the bellow code chunk. 
```{r}
inspect(corpus)
```
Also, we can check specific metada unsing the __meta__ for the entire corpus (in our case 3 documents) or we can bem more specific and specify wich document we want to extract the metadata 

```{r}
meta(corpus,"language")
meta(corpus[2],"id")
```

So, after loading the corpus, its necessary to clean up it a bit in order to remove "noisy information" such as numbers, special characters, and so on... I will ommit the results of the next chunk to be a little more consice on this report.

```{r, message=FALSE, warning=FALSE, include=FALSE}
corpus <- tm_map(corpus,content_transformer(tolower))
corpus <- tm_map(corpus,removeWords,stopwords("de"))
corpus <- tm_map(corpus,stripWhitespace)
corpus <- tm_map(corpus,stemDocument)
corpus <- tm_map(corpus,removeNumbers)
corpus <- tm_map(corpus,removePunctuation)

```

I choose to generate a DocumentTermMatrix to first explore the corpus, since it, already calculate several aspect such as term frequency, sparsity among possible others. The matrix generation is quite resource demanding and take some time, that's why I had to short the raw data in shorter version. Otherwise Im unable to generate the data matrix.

```{r}

BigramTokenizer <- function(x) NGramTokenizer(x, Weka_control(min = 2, max = 2))

termMatrix <- TermDocumentMatrix(corpus, 
                          control =  list(tokenize = BigramTokenizer,
                                          language="german",
                                          removeNumbers=TRUE,
                                          stemming=TRUE,
                                          stopwords=TRUE
                                          )
                          )



```


## Visualizations

So, while learning about NLP and TM, I find a visualization practice named **"wordclod"** which is somewhat a interesting visualiztion to approach a new text-based dataset.

```{r }
require(wordcloud)

mtrx <- as.matrix(termMatrix)
freq <- sort (rowSums (mtrx))
tmdata <- data.frame (words=names(freq), freq)

```


```{r}
wordcloud (tmdata$words, tmdata$freq, random.order=FALSE, colors=brewer.pal(8, "Dark2"))

```


And also some text clustering , and bigram frequency histogram.
```{r}
f <- matrix (0, ncol=nrow(mtrx), nrow=nrow(mtrx)) 
colnames (f) <- rownames(mtrx)
rownames (f) <- rownames(mtrx)

for (i in rownames (Matrix)) {

  ff <- findAssocs (Matrix,i,0)

  for  (j in rownames (ff)) {

    f[j,i]=ff[j,]

  }

}

fd <- as.dist(f)

```


```{r}
plot(hclust(fd, method="ward")) 

```


