---
title: 'Data Science Capstone Report #1'
author: "José Gustavo Zagato Rosa"
date: "07/05/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Milestone Report 
### Introduction and Objectives

The main goal of this report is to demonstrate the the capacity developed to handle unstructred data in order to produce a structured set of records which can then be used for the purposes of statistical modeling in the relms of Text Mining. 

Due the size of the provided raw files I took the approach to structure different scripts to handle specific steps of the entire process. for more detais, please refer to my gitrepo wich contains the whole project. [getrepo](https://github.com/jguszr/DSCapstone)

I also tried to use as much as possible of the  [TM R](https://cran.r-project.org/web/packages/tm/index.html)  package among with its plugins for multicore processing (which, at this time I still developing).

### The Process

I approach this project from a streamline point of view, in which I separete different objectives in diferent files. So at this point the project contains 4 folder structures as follows

* **data** : Contains a individual folder for each step of the process, from raw file to Ngram Files
* **Prepare** : Contains the R Scripts to download and setup the local systems *data* structure and split the raw data into smaller sampler files. the File itself can be found [here](https://github.com/jguszr/DSCapstone/blob/master/Prepare/prepareData.R)

* **Exploratory** : Contains the R Scripts That I used to learn the TM package among some preliminary studies regarding the data it self. 

* **Exploratory** : Contains the R Scripts That I used to learn the TM package among some preliminary studies regarding the data it self. check the file [here](https://github.com/jguszr/DSCapstone/blob/master/Exploratory/CorseExplorer.R)

* **ngramGennerator** : Contains the R Scripts That I used to process the short files (previously generated by the Prepare script) into DocumentTermMatrix into three new CVS files containing the frequency of the most comon Ngram in question.[here](https://github.com/jguszr/DSCapstone/blob/master/ngramGennerator/nGramGenerator.R)

### The overall process 

Idealistically you can run the scripts in the following squence to archive the same result I got.

* **Prepare** : [Prepare everything] (https://github.com/jguszr/DSCapstone/blob/master/Prepare/prepareData.R)

* **ngramGennerator** : [Generate the Ngrams] (https://github.com/jguszr/DSCapstone/blob/master/Prepare/prepareData.R)

This two steeps will get the __.cvs__ files containg Ngram frequencies.


## And now some initial analisys

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
